The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex

             If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, in that order.
             If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.

>>>>

             If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, in that order.
             If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf. \cite{ShibutaTakagiLCThresholds}).
